### 2016-11-08 text/ms.Rmd
Update addresses
Copyediting

\noindent ^10^European Commission, Joint Research Centre, Institute for the
Protection and Security of the Citizen, Maritime Affairs Unit G03, Via E. Fermi
2749, 21027 Ispra (VA), Italy

@@

Combining predictions from multiple models via superensemble methods is broadly
useful in other subfields of fisheries science and ecology in general.
\R{A}In fisheries science, superensembles provide an 
additional tool to assist with some longstanding issues.
For example, superensembles assist since modelers need not 
decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could help assess overfishing by estimating 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or be trained to estimate natural mortality.

>>>>

\noindent ^10^European Commission, DG Joint Research Centre, Directorate D --
Sustainable Resources, Unit D.02 Water and Marine Resources, Via E. Fermi 2749,
21027 Ispra VA, Italy

@@

Combining predictions from multiple models via superensemble methods is broadly
useful in other subfields of fisheries science and ecology in general.
\R{A}In fisheries science, superensembles provide an 
additional tool to assist with some longstanding issues.
For example, superensembles are helpful since modelers need not 
decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could help assess overfishing by estimating 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or be trained to estimate natural mortality.
